Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-21 paper.tex
Pass on the abstract

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
Learning social interaction is a complex task. Firstly, no simulator of
human interactions sufficiently precise exists today, so the learning will probably have
to be made online and in the real world.
This means that robots will have to learn directly from interacting with humans,
which limits the quantity of datapoint possible to gather and make exploration
riskier as actions will have real impacts on humans or the robot itself. Additionally,
no clear reward function exists for social interactions. As such we argue that
robots will highly profit from human expertise and guidance to learn social
interactions. And as the quantity of data is limited, they also will have to make the most out of each datapoint. We
propose to combine the Supervised Progressively Autonomous Robot Competencies
allowing a safer online learning and Reinforcement Learning based on partial
states rather than full states to accelerate the learning by using more
information form the human teacher.
\end{abstract}
%===============================================================================

>>>>

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
    Learning social interactions is a complex task that robots will have to
    master before being accepted in society. However, as no simulator of human
    interactions sufficiently
    precise exists today, the learning have to be made online and in the real
    world. Actions executed by the robot have impact on humans, and as such
    have to be carefully selected, making the reliance on random exploration not
    applicable. Additionally, no clear reward function exists for
    social interactions. This implies that classical approaches such as
    Reinforcement Learning cannot be directly applied. As such we argue that
    robots will highly profit from human expertise and guidance to learn social
    interactions. And as the quantity of input a human can provide is limited,
    new methods have to be designed to use more efficiently human inputs. We
    combine the Supervised Progressively Autonomous Robot Competencies (SPARC)
    allowing a safer online learning with Reinforcement Learning based on
    partial states rather than full states to accelerate the learning by
    collecting and using more information from the human teacher.
\end{abstract}
%===============================================================================
